No need to know: astrophysics-agnostic spectral siren cosmology

### 2024-02-14 src/tex/ms.tex
[showyourwork] overleaf sync

This result also implies that we can expect to measure \Ho{} to \result{X\%} by the end of the LVK's fifth observing run using this method.

>>>>

This result also implies that we can expect to measure \Ho{} to \result{\variable{output/nonparh0percent.txt}\%} by the end of the LVK's fifth observing run using this method.
